The impact of gas bulk rotation on the Lyman-$\alpha$ line

### 2013-10-13 paper/Analisis.tex
Delelted OC_5t_vel100.jpg

\begin{figure}
\includegraphics[scale=0.3]{OC_5t_vel100.jpg}
\caption{Spectra for two off-center spheres
   \label{fig:OCspectra}} 
\end{figure}

@@

... Comparison with Verhamme et al. results on the rotation (Viewing angle)

... Compare with Kulas et al (Figure 3), Rotation on the lyman alpha
line convert double peak profiles into a single one. comments about
rotation with inflows and outflows.

>>>>

%\begin{figure}
%\includegraphics[scale=0.3]{OC_5t_vel100.jpg}
%\caption{Spectra for two off-center spheres
%   \label{fig:OCspectra}} 
%\end{figure}

@@

Comparing with the sample of (Kulas et al) we observe that rotational effects could be 
associated in group IV and V in galaxies where the difference between the two peaks is 
small and .

No effects asociated with inflows or outflows
